Analysis : exp249-253 analysis

### 2019-08-19 resistingrhythm/analysis/exp328-339.Rmd
Added H only + gamma only plots

```{r, fig.height=2.5, fig.width=2.25}
results %>% 
  filter(osc_rate < 1.5, freq < 150) %>% 
  ggplot(aes(x=osc_rate, y=rate_k, group=interaction(osc_rate, homeo), color=homeo)) +
  geom_boxplot() +
  theme_classic() +
  scale_color_grey() +
  facet_grid(freq~kind, scales = "free")
```

>>>>

```{r, fig.height=2, fig.width=2.25}
results %>% 
  filter(osc_rate < 1.5, freq < 150, freq > 8) %>% 
  ggplot(aes(x=osc_rate, y=rate_k, group=interaction(osc_rate, homeo), color=homeo)) +
  geom_boxplot() +
  theme_classic() +
  scale_color_grey() +
  lims(y=c(0, 150)) +
  facet_grid(kind~freq, scales = "free")
```

# H only plots
```{r, fig.height=1.3, fig.width=2.5}
results %>% 
  filter(osc_rate < 1.5, freq < 150, freq > 8) %>% 
  filter(homeo == "Homeostasis") %>% 
  ggplot(aes(x=as.factor(osc_rate), y=rate_k, group=interaction(osc_rate, kind), color=kind)) +
  geom_boxplot() +
  theme_classic() +
  scale_color_manual(values=c("darkgoldenrod3", "black"), name="Oscillation") +
  # lims(y=c(0, 100)) +
  labs(y="Pop. rate", x="Osc. rate", tag="a.") +
  facet_grid(.~freq, scales = "free")
```

```{r, fig.height=1.3, fig.width=2.5}
results %>% 
  filter(osc_rate < 1.5, freq < 150, freq > 8) %>% 
  filter(homeo == "Homeostasis") %>% 
  ggplot(aes(x=as.factor(osc_rate), y=kappa_coord, group=interaction(osc_rate, kind), color=kind)) +
  geom_boxplot() +
  theme_classic() +
  scale_color_manual(values=c("darkgoldenrod3", "black"), name="Oscillation") +
  # lims(y=c(0.0, .12)) +
  labs(y="Kappa", x="Osc. rate", tag="b.") +
  facet_grid(.~freq, scales = "free")
```
